Blocking-resistant communication\\through domain fronting

### 2014-07-15 docs/meek.tex
Comment out obfs-flash.

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies. Proxies last only as long as a web
user stays on a page, so the pool of proxies is constantly changing;
even if one of them is blocked, there will soon be another to replace it.
Flash proxy's approach to address blocking is in a sense
the opposite of ours: where flash proxy uses cheap, disposable, individually blockable proxies,
we use just one high-value proxy, which shares its fate with network
infrastructure that is expensive to block.
A quirk of the browser proxy model is that the proxy connects to the client rather than the other way around.
The client must be able to receive a TCP connection; in particular it
may not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Flash proxy itself does nothing to defend against content blocking.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on TCP,
but inside the WebSocket framing is the ordinary Tor protocol.
There exists a prototype transport that attempts to get both
content-based and address-based blocking resistance by obfuscating traffic
with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
However it is limited because it is not
possible to obfuscate the outermost WebSocket layer;
the censor could decide simply to block all WebSocket.

>>>>

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies. Proxies last only as long as a web
user stays on a page, so the pool of proxies is constantly changing;
even if one of them is blocked, there will soon be another to replace it.
Flash proxy's approach to address blocking is in a sense
the opposite of ours: where flash proxy uses cheap, disposable, individually blockable proxies,
we use just one high-value proxy, which shares its fate with network
infrastructure that is expensive to block.
A quirk of the browser proxy model is that the proxy connects to the client rather than the other way around.
The client must be able to receive a TCP connection; in particular it
may not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Flash proxy itself does nothing to defend against content blocking.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on TCP,
but inside the WebSocket framing is the ordinary Tor protocol.
% There exists a prototype transport that attempts to get both
% content-based and address-based blocking resistance by obfuscating traffic
% with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
% However it is limited because it is not
% possible to obfuscate the outermost WebSocket layer;
% the censor could decide simply to block all WebSocket.
